Statistical performance analysis of data-driven neural mass models

### 2013-09-19 manuscript/manuscript.tex
Included plot of CRB vs time

The model focused on in the following
estimation sections is the formulation by Jansen and Rit \cite{Jansen-Rit-95}.
Given space limitations we refer the reader to the article by Jansen
and Rit\cite{Jansen-Rit-95} where the original state-space equations
are presented. The parameters that were described in this section are related to the Jansen and Rit paper by
\begin{align}
    A =& \frac{\alpha_{pe}}{2e_0c_1} = \frac{\alpha_{pi}}{2e_0c_3} = \frac{\alpha_{ep}}{2e_0c_2} = \frac{\alpha_{xp}}{2e_0} \\
    B =& \frac{\alpha_{ip}}{2e_0c_4} \\
    a =& \frac{1}{\tau_{pe}} = \frac{1}{\tau_{pi}} = \frac{1}{\tau_{ep}} = \frac{1}{\tau_{xp}} \\
    b =& \frac{1}{\tau_{ip}},
\end{align}
where $e_0$ is a parameter that scales the maximum firing rate, $A$ and $B$ are synaptic gains for excitation and inhibition respectively, and $a$ and $b$ are the reciprocals of the synaptic time constants for excitation and inhibition, respectively, and the subscripts $p$, $e$, $x$, and $i$ denote pyramidal ($p$), excitatory interneuron (spiny stellate) ($e$), external ($x$) or inhibitory interneuron ($i$) populations, respectively. By making the assumption that all excitatory synapses share the same time constants and by defining the connectivity constants, $c_1$, $c_2$, $c_3$ and $c_4$, the network of neural masses is the JR NMM.

@@

To provide some intuition into the Bayes information matrix, we can write the joint distribution $p(\vec y,\vec x)$ as the product of the likelihood function and the prior distribution. Taking the logarithm gives
\begin{align}
	\log p(\vec y,\vec x) =& \log\mathcal{L}(\vec x|\vec y) + \log p(\vec x).
\end{align}
Using this relation, the Bayes information matrix in \eqref{eqn:bayes_matrix} can be decomposed into a data component, $\mat J_D$, and a prior component, $\mat J_P$, such that $\mat J = \mat J_D + \mat J_P$.
The two components are defined as
\begin{align}
	\mat J_D &= \mathbb E_{\vec x}\left[ \mat J_F(\vec x) \right]  \\
	\mat J_P &= -\mathbb E_{\vec x}\left[ \nabla_{\vec x}\nabla_{\vec x}^T \log p(\vec x) \right]
\end{align}
where $\mat J_F$ is the classical Fisher information matrix for deterministic states,
\begin{align}
	\mat J_F(\vec x) &= -\mathbb E_{\vec y| \vec x}\left[ \nabla_{\vec x}\nabla_{\vec x}^T \log p(\vec y|\vec x) \right].
\end{align}
Some important insights can be gained from this decomposition. First, the contribution of the data to the Bayes information matrix is the expectation of the classical Fisher information matrix taken over all possible states. Secondly, the contribution from the prior distribution directly adds to the Bayes information matrix, capturing our prior knowledge about of the states.

>>>>

\unit{Is the following paragraph needed? -}
The model focused on in the following
estimation sections is the formulation by Jansen and Rit \cite{Jansen-Rit-95}.
Given space limitations we refer the reader to the article by Jansen
and Rit\cite{Jansen-Rit-95} where the original state-space equations
are presented. The parameters that were described in this section are related to the Jansen and Rit paper by
\begin{align}
    A =& \frac{\alpha_{pe}}{2e_0c_1} = \frac{\alpha_{pi}}{2e_0c_3} = \frac{\alpha_{ep}}{2e_0c_2} = \frac{\alpha_{xp}}{2e_0} \\
    B =& \frac{\alpha_{ip}}{2e_0c_4} \\
    a =& \frac{1}{\tau_{pe}} = \frac{1}{\tau_{pi}} = \frac{1}{\tau_{ep}} = \frac{1}{\tau_{xp}} \\
    b =& \frac{1}{\tau_{ip}},
\end{align}
where $e_0$ is a parameter that scales the maximum firing rate, $A$ and $B$ are synaptic gains for excitation and inhibition respectively, and $a$ and $b$ are the reciprocals of the synaptic time constants for excitation and inhibition, respectively, and the subscripts $p$, $e$, $x$, and $i$ denote pyramidal ($p$), excitatory interneuron (spiny stellate) ($e$), external ($x$) or inhibitory interneuron ($i$) populations, respectively. By making the assumption that all excitatory synapses share the same time constants and by defining the connectivity constants, $c_1$, $c_2$, $c_3$ and $c_4$, the network of neural masses is the JR NMM.

@@

To provide some intuition into the Bayes information matrix, we can write the joint distribution $p(\vec y,\vec x)$ as the product of the likelihood function, $\mathcal L$, and the prior distribution, $p_0$. Taking the logarithm gives
\begin{align}
	\log p(\vec y,\vec x) =& \log\mathcal{L}(\vec x|\vec y) + \log p_0(\vec x).
\end{align}
Using this relation, the Bayes information matrix in \eqref{eqn:bayes_matrix} can be decomposed into a data component, $\mat J_D$, and a prior component, $\mat J_P$, such that $\mat J = \mat J_D + \mat J_P$.
The two components are defined as
\begin{align}
	\mat J_D &= \mathbb E_{\vec x}\left[ \mat J_F(\vec x) \right]  \\
	\mat J_P &= -\mathbb E_{\vec x}\left[ \nabla_{\vec x}\nabla_{\vec x}^T \log p_0(\vec x) \right]
\end{align}
where $\mat J_F$ is the classical Fisher information matrix for deterministic states,
\begin{align}
	\mat J_F(\vec x) &= -\mathbb E_{\vec y| \vec x}\left[ \nabla_{\vec x}\nabla_{\vec x}^T \log p(\vec y|\vec x) \right].
\end{align}
Some important insights can be gained from this decomposition. First, the contribution of the data to the Bayes information matrix is the expectation of the classical Fisher information matrix taken over all possible states. Secondly, the contribution from the prior distribution increases the Bayes information matrix, capturing our prior knowledge about of the states.
